Self Regulation Ontology Retest Data Report

### 2018-03-12 code/SRO_Report.Rmd
updating based on draft comments

```{r warning=FALSE, message=FALSE}
boot_df %>%
  ggplot(aes(icc, fill = task))+
  geom_histogram(alpha=0.5, position='identity')+
  theme_bw()+
  theme(legend.title = element_blank())+
  xlab("ICC")

ggsave('Hist_Boot_Rel.jpg', device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/", width = 6, height = 4, units = "in", limitsize = FALSE, dpi = 72)
```

@@

```{r}
tmp %>%
  gather(key, value, -dv, -task) %>%
  group_by(task, key) %>%
  ggplot(aes(factor(task, levels=c("task","survey"), labels=c("Task", "Survey")), value, fill=task, alpha=key))+
  geom_boxplot()+
  theme_bw()+
  theme(legend.title = element_blank())+
  scale_alpha_manual(breaks = c("var_subs_pct", "var_ind_pct", "var_resid_pct"),
                    labels = c("Variance between individuals",
                               "Variance between sessions",
                               "Error variance"),
                    values=c(0.1, 0.5, 1))+
  scale_fill_discrete(guide = FALSE)+
  guides(alpha=guide_legend(override.aes=list(fill=hcl(c(15,195),100,0,alpha=c(0.1,0.5, 1)),
                                              colour=NA)))+
  xlab("")+
  ylab("Percent")

ggsave('Variance_Breakdown_Plot_Summary.jpg', device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures", width = 10, height = 5, units = "in", dpi = 100)
```

```{r}
tmp %>%
  gather(key, value, -dv, -task) %>%
  group_by(task, key) %>%
  summarise(mean_pct = mean(value),
            sd_pct = sd(value))
```

@@

```{r warning=FALSE, message=FALSE}
tmp = measure_labels %>%
  mutate(dv = as.character(dv)) %>%
  filter(task == 'task') %>%
  left_join(boot_df[,c("dv", "icc", "spearman")], by = 'dv') %>%
  filter(overall_difference != 'difference' & raw_fit %in% c('EZ', 'hddm') == FALSE)%>%
  separate(dv, c('task_name', 'extra_1', 'extra_2'), sep = '\\.',remove=FALSE) %>%
  select(-extra_1, -extra_2) %>%
  group_by(task_name) %>%
  summarise(median_icc = median(icc),
            median_spearman = median(spearman),
            min_icc = min(icc),
            max_icc = max(icc),
            min_spearman = min(spearman),
            max_spearman = max(spearman),
            num_measures = n()/1000,
            num_trials = unique(num_all_trials))%>%
  arrange(-median_icc, -median_spearman)

@@

```{r warning=FALSE, message=FALSE}
#read t1 data
t1_hr = read.csv(gzfile(paste0(test_data_path,'Individual_Measures/hierarchical_rule.csv.gz'), 'rt'))

t2_hr = read.csv(gzfile(paste0(retest_data_path,'Individual_Measures/hierarchical_rule.csv.gz'), 'rt'))

#get only retest subjects
t1_hr = t1_hr[as.character(t1_hr$worker_id) %in% as.character(test_data$sub_id),]
t2_hr = t2_hr[as.character(t2_hr$worker_id) %in% as.character(retest_data$sub_id),]

#remove missed trials (rt == -1)
t1_hr = t1_hr %>% filter(rt != -1)
t2_hr = t2_hr %>% filter(rt != -1)

#dv's
#accuracy: mean correct
#average rt: median of correct trials only
#score: sum correct

calc_break_dvs = function(x, breaks=seq(0, 360, 10)[-1]){

  calc_dvs = function(x){
    out = x %>%
      summarise(acc = mean(correct),
                avg_rt = median(rt[correct == 1]))
                # score = sum(correct))
    return(out)
  }

@@

  for(i in 1:length(breaks)){
    tmp = x[1:breaks[i],]
    dvs = calc_dvs(tmp)
    out = rbind(out, dvs)
  }

  # due to timeout trials exclusion not all subjects might have 360 rows
  # this would lead to na's for later trial breaks
  # first remove these
  out = out %>% drop_na()

  # then calculate the dv's for the remaining trials
  if(nrow(x)!=360 & nrow(x)%%10 != 0){
    dvs = calc_dvs(x)
    out = rbind(out, dvs)
  }

@@

#get dv's for t1 and t2
t1_dvs = t1_hr %>%
  group_by(worker_id) %>%
  do(calc_break_dvs(.)) %>%
  rename(sub_id = worker_id)

t2_dvs = t2_hr %>%
  group_by(worker_id) %>%
  do(calc_break_dvs(.)) %>%
  rename(sub_id = worker_id)

>>>>

@@

```{r}
tmp %>%
  gather(key, value, -dv, -task) %>%
  group_by(task, key) %>%
  summarise(mean_pct = mean(value),
            sd_pct = sd(value),
            n = n()) %>%
  mutate(cvl = qt(0.025, n-1),
         cvu = qt(0.975, n-1),
         cil = mean_pct+(sd_pct*cvl)/sqrt(n),
         ciu = mean_pct+(sd_pct*cvu)/sqrt(n)) %>%
  ggplot(aes(factor(key, levels = c("var_subs_pct", "var_ind_pct", "var_resid_pct"),
                    labels = c("Variance between individuals",
                               "Variance between sessions",
                               "Error variance")), mean_pct, color=task))+
  geom_point(position=position_dodge(width = 0.25), size=5)+
  geom_errorbar(aes(ymin=mean_pct-sd_pct, ymax=mean_pct+sd_pct), position=position_dodge(width = 0.25), width=0, size=2)+
  theme_bw()+
  xlab('')+
  ylab('Percent')+
  theme(legend.title = element_blank(),
        legend.text = element_text(size=14),
        axis.text = element_text(size=12),
        axis.title.y = element_text(size=12))+
  scale_x_discrete(labels = function(x) str_wrap(x, width = 15))

ggsave('Variance_Breakdown_DotPlot.jpg', device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures", width = 6, height = 5, units = "in", dpi = 100)
```

@@

```{r warning=FALSE, message=FALSE}
tmp = measure_labels %>%
  mutate(dv = as.character(dv)) %>%
  filter(task == 'task') %>%
  left_join(boot_df[,c("dv", "icc", "spearman")], by = 'dv') %>%
  filter(overall_difference != 'difference' & raw_fit %in% c('EZ', 'hddm') == FALSE)%>%
  separate(dv, c('task_name', 'extra_1', 'extra_2'), sep = '\\.',remove=FALSE) %>%
  select(-extra_1, -extra_2) %>%
  group_by(task_name) %>%
  summarise(median_icc = median(icc),
            median_spearman = median(spearman),
            min_icc = min(icc),
            max_icc = max(icc),
            min_spearman = min(spearman),
            max_spearman = max(spearman),
            num_measures = n()/1000,
            mean_num_trials = round(mean(num_all_trials)))%>%
  arrange(-median_icc, -median_spearman)

@@

```{r warning=FALSE, message=FALSE}
#read t1 data
t1_tbt = read.csv(gzfile(paste0(test_data_path,'Individual_Measures/threebytwo.csv.gz'), 'rt'))

t2_tbt = read.csv(gzfile(paste0(retest_data_path,'Individual_Measures/threebytwo.csv.gz'), 'rt'))

#get only retest subjects
t1_tbt = t1_tbt[as.character(t1_tbt$worker_id) %in% as.character(test_data$sub_id),]
t2_tbt = t2_tbt[as.character(t2_tbt$worker_id) %in% as.character(retest_data$sub_id),]

#dv's
calc_break_dvs = function(df, breaks=c(seq(0, 440, 10)[c(-1, -45)], 439)){

  df = df %>%
      filter(exp_stage != "practice")

  calc_dvs = function(df){

    df = df %>%
      mutate(correct_shift = lag(correct),
             task_switch_shift = lag(task_switch))

    missed_percent = mean(df$rt == -1)

     df = df %>%
      filter(rt != -1)

     df_correct = df %>%
       filter(correct == "True" & correct_shift == "True")

     dvs = data.frame(acc = mean(ifelse(df$correct == "True",1,0)),
                      avg_rt_error = median(df$rt[df$correct == "False"]),
                      std_rt_error = sd(df$rt[df$correct == "False"]),
                      avg_rt = median(df_correct$rt),
                      std_rt = sd(df_correct$rt),
                      missed_percent = missed_percent)

     cue_switch_cost_rt_df = df_correct %>% group_by(CTI, cue_switch) %>% summarise(cue_switch_cost = median(rt)) %>% complete(cue_switch, CTI) %>% filter(cue_switch %in% c("stay", "switch")) %>% ungroup() %>% spread(cue_switch,cue_switch_cost) %>% group_by(CTI) %>% summarise(cue_switch_cost_rt = switch-stay)

     dvs$cue_switch_cost_rt_100 = cue_switch_cost_rt_df$cue_switch_cost_rt[cue_switch_cost_rt_df$CTI == 100]
     dvs$cue_switch_cost_rt_900 = cue_switch_cost_rt_df$cue_switch_cost_rt[cue_switch_cost_rt_df$CTI == 900]

     task_switch_rt = df_correct %>% mutate(task_switch = factor(ifelse(grepl("switch",task_switch), T, F))) %>% group_by(CTI, task_switch) %>% summarise(rt = median(rt)) %>% complete(task_switch, CTI) %>% ungroup() %>% filter(task_switch == T)

     cue_switch_rt = df_correct %>% group_by(CTI, cue_switch) %>% summarise(rt = median(rt)) %>% complete(cue_switch, CTI) %>% ungroup() %>% filter(cue_switch == "switch")

     dvs$task_switch_cost_rt_100 = task_switch_rt$rt[task_switch_rt$CTI == 100] - cue_switch_rt$rt[cue_switch_rt$CTI == 100]

     dvs$task_switch_cost_rt_900 = task_switch_rt$rt[task_switch_rt$CTI == 900] - cue_switch_rt$rt[cue_switch_rt$CTI == 900]

     cue_switch_cost_acc_df = df %>% group_by(CTI, cue_switch) %>% summarise(acc = mean(ifelse(correct == "True",1, 0))) %>% complete(cue_switch, CTI) %>% filter(cue_switch %in% c("stay", "switch")) %>% spread(cue_switch, acc) %>% ungroup() %>% group_by(CTI) %>% summarise(cue_switch_cost_acc = switch-stay)

     dvs$cue_switch_cost_acc_100 = cue_switch_cost_acc_df$cue_switch_cost_acc[cue_switch_cost_acc_df$CTI == 100]
     dvs$cue_switch_cost_acc_900 = cue_switch_cost_acc_df$cue_switch_cost_acc[cue_switch_cost_acc_df$CTI == 900]

     task_switch_acc = df %>% mutate(task_switch = factor(ifelse(grepl("switch",task_switch), T, F))) %>% group_by(CTI, task_switch) %>% summarise(acc = mean(ifelse(correct == "True",1,0))) %>% complete(task_switch, CTI) %>%  ungroup() %>% filter(task_switch == T)

     cue_switch_acc = df %>% group_by(CTI, cue_switch) %>% summarise(acc = mean(ifelse(correct == "True",1,0))) %>% complete(cue_switch, CTI) %>% ungroup() %>% filter(cue_switch == "switch")

     dvs$task_switch_cost_acc_100 = task_switch_acc$acc[task_switch_acc$CTI == 100] - cue_switch_acc$acc[cue_switch_acc$CTI == 100]

     dvs$task_switch_cost_acc_900 = task_switch_acc$acc[task_switch_acc$CTI == 900] - cue_switch_acc$acc[cue_switch_acc$CTI == 900]

    return(dvs)
  }

@@

  for(i in 1:length(breaks)){
    tmp = df[1:breaks[i],]
    dvs = calc_dvs(tmp)
    out = rbind(out, dvs)
  }

  # due to timeout trials exclusion not all subjects might have 360 rows
  # this would lead to na's for later trial breaks
  # first remove these
  # out = out %>% drop_na()

  # then calculate the dv's for the remaining trials
  if(nrow(df)!=440 & nrow(df)%%10 != 0){
    dvs = calc_dvs(df)
    out = rbind(out, dvs)
  }

@@

#get dv's for t1 and t2
t1_dvs = t1_tbt %>%
  group_by(worker_id) %>%
  do(calc_break_dvs(.)) %>%
  rename(sub_id = worker_id)

t2_dvs = t2_tbt %>%
  group_by(worker_id) %>%
  do(calc_break_dvs(.)) %>%
  rename(sub_id = worker_id)
